---
title: "Please select your title"
author:
- familyname: XXXX
  othernames: XXX
  address: Monash Universtidy
  email: XXX
  correspondingauthor: true
  qualifications:  XXX
- familyname: XXXX
  othernames: XXX
  address: Monash Universtidy
  email: XXX
  correspondingauthor: true
  qualifications:  XXX
- familyname: Wei
  othernames: Juntong
  address: Monash Universtidy
  email: jwei55@student.monash.edu
  correspondingauthor: true
  qualifications:  Master
- familyname: Xu
  othernames: Qin 
  address: 40 Carboni crescent 
  email: qxuu0023@student.monash.edu
  correspondingauthor: true
  qualifications:  Mbat
department: Our consultancy \newline add names &\newline add names
organization: Australian Government COVID19
bibliography: references.bib
biblio-style: authoryear-comp
linestretch: 1.5
output:
  bookdown::pdf_document2:
    template: monashreport2.tex
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: false
---

```{r , echo = FALSE, message = FALSE, warning = FALSE}
# Libraries

library(tidyverse)
library(readr)
library(kableExtra)
```



\section*{Country XX1 and YY1"}

\section*{Country XX2 and YY2}
```{r}
library(tidyverse)
library(kableExtra)
```

```{r}
dat <- read.csv("Assignment3_data.csv")
dat1 <- dat %>%
  filter(Country_Name %in% c("China",
                             "Japan")) %>%
  group_by(Country_Name) %>%
  summarise(CO2 = sum(CO2_emissions_metric_tons_per_capita))
kable(dat1)
```

\section*{Country XX3 and YY3}

```{r}
data <- read.csv("Assignment3_data.csv") %>% 
  filter(Country_Name == "Japan" | Country_Name == "Australia") %>% 
  group_by(Country_Name)
data
#df <- data %>% 
  #summarise(Average_population = mean(Urban_population))
#df
```
The result of this table illustrate that ......

\section*{Country Australia and India}

```{r}
knitr::opts_chunk$set(echo = FALSE, 
                      cache = FALSE, 
                      cache.lazy = FALSE,
                      eval = TRUE,
                      fig.align= "center")

```

```{r}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(dslabs)
library(kableExtra)
library(bookdown)
library(knitr)
```

```{r}
data <- read.csv("Assignment3_data.csv")
head (data)
glimpse(data)
dim(data)
data
```

## Comparsion of OF CO2 emission between Australia and India


```{r table1}
countries_urban <- data %>% 
  group_by(Country_Name) %>% 
    filter (Country_Name == "Australia" | Country_Name == "India" ) %>% 
  select(-c("Year","Region","CO2_emissions_metric_tons_per_capita","Energy_use_kg_of_oil_equivalent_per_capita")) %>% 
  summarise ( Urban_population = sum(Urban_population, na.rm=TRUE)) %>% 
  arrange(desc(Urban_population))
countries_urban

knitr::kable (countries_urban ,caption = "The total Urban_population from 1960 to 2014 for both Australia and India") %>% kable_styling()
```
In Table \@ref(tab:table1) we compare the Urban_population of India and Australia from 1960 to 2014. 

```{r urban, fig.cap = "Comparison of Urban_population of India and Australia from 1960 to 2014."}
plot_urban<- ggplot(data = countries_urban, 
                      aes(x = Country_Name,
                          y= Urban_population,
                          fill= Country_Name)) +

               geom_col()
plot_urban
```
In Figure \@ref(fig:urban), we have plotted the total number of urban population for india and Australia from 1960 to 2014.

From the table above, we can see that the urban population for India is 13754306693 where as the urban population for Australia is 849155686. The plot above also shows a siginificant difference in urabn population between the two country, with India's urban population being much more higher compared to Australia.

```{r}
co2_emission <- data %>% 
  filter( Country_Name =="Australia" |Country_Name =="India") %>% 
  select (c("Country_Name","CO2_emissions_metric_tons_per_capita","Year" )) 
  
co2_emission

```


